\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-04-17 jss/article.tex
corrections

%% an abstract and keywords
\Abstract{Bayesian-frequentist reconciliation via Bayesian hierarchical modeling for Gaussian, Binomial, and Poisson data and frequentist method check for good coverage probability.}
\Keywords{hierarchical model, multi-level model, random effects mixed model, method check, coverage probability, normal, binomial, poisson, shrinkage, \proglang{R}}
\Plainkeywords{keywords, comma-separated, not capitalized, r} %% without formatting
%% at least one keyword must be supplied

@@

\section[Feasible Data Types]{Three Feasible Types of Data }
This package is intended to fit a multi-level model on the group-level (or unit-level) data in which each group-level (or unit-level) observation is believed to have the Normal, Poisson, or Binomial distribution. In this section, we will introduce three specific types of feasible datasets.

@@

\section[Multi-level Structure]{Multi-level Structure}
Our multi-level model, also called a conditionally independent hierarchical model (Kass and Steffey, 1989), is a very powerful tool for exploring the hierarchical sturucture in data. For example, we can think about a district-level hierarchy (bigger population) for 8 schools, the state-level hierarchy for 31 hospitals, and the position-level hierarchy for 18 baseball players. \code{gbp}, one of functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate prior distribution on the first-level parameter. Users can determine one of three types of multi-level models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their datasets. 
\\

@@

where $\mu_{0j} =x^{T}_{j}\beta,~j=1, \ldots, 8$, $x_{j}$ is $j$-th school's covariate vector ($m\times 1$), and $m$ is the number of regression coefficients. Note that if there is no covariate then $x_{j, (1\times1)}=1$ for an intercept term and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution. For reference, a paramter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean. Also,  Based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution, which is the same as (1) $\times$ (2) up to a normalizing constant.
\begin{equation}
\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})\sigma^{2}_{j}),
\end{equation}
where $B_{j}\equiv\frac{\sigma^{2}_{j}}{\sigma^{2}_{j} + A},~j=1, \ldots, 8$, is called a shrinkages.

\subsection[Poisson-Gamma]{Poisson-Gamma}
\code{gbp} is also able to build a Poisson-Gamma multi-level model on the 31 hospital data. Note that a constant, $1/r$, multiplied to the Gamma distribution below is a scale and a square bracket below indicates [mean, variance] of distribution. And for notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ for all $j$.
\begin{equation}
z_{j}\vert \lambda_{j} \stackrel{ind}{\sim}\textrm{Poisson}(n_{j}\lambda_{j}),
\end{equation}
\begin{equation}
\lambda_{j}\vert \beta, r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(\lambda_{0j}r)\sim \textrm{Gamma}[\lambda_{0j}, ~\frac{\lambda_{0j}}{r}],
\end{equation}

@@

\subsection[ADM]{Adjustment for Density Maximization}
When it comes to estimating a shrinkage, we can notice that it is a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv\frac{\sigma^{2}}{\sigma^{2}+A}=B_{j}(A)$ for Gaussian and $B_{j}\equiv\frac{r}{r+n_{j}}=B_{j}(r)$ for Poisson and Binomial models.
\\

In this case, the most common way is to obtain an MLE of the variance component with its asymptotic Normality and then to use Delta method for asymptotic Normal distribution of shrinkage, \emph{i.e.}, $\hat{B}_{j, MLE}=B_{j}(\hat{A}_{MLE})$. But is the Normal approximation a good approximation for shrinkage that takes on a value between 0 and 1? Why do we fit a logistic regression, such as logit($p$) = $x^{T}\beta$, instead of fitting a linear regression, $p = x^{T}\beta$?
\\

Here the adjustment for density maximization (Morris and Tang, 2011), called ADM, comes. It assumes the Beta distribution for shrinkage because this distribution is also defined between 0 and 1. In the end, ADM  estimates its posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without any trouble that MLE can cause. Please refer to Morris and Tang (2011) for more apparent advantages for using ADM.
\\

@@

There are two kinds of model justification process; one is a model check and the other is a method check. The model check is for the justification of a hierarchical modeling on a specific dataset. One possible question is, ``Can this dataset benefit from such a multi-level modeling?'' Christiansen and Morris (1996) answered this question by using a mixture model, $z_{j}\vert \beta, r\sim\textrm{Negative-Binomial}$, on Poisson data to justify the second-level hierarchy. They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
\\

Once we are sure that the hierarchical modeling can be appropriate for our data, the following quetsion will be about the validity of interval estimates, the final product of this multi-level modeling. ``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to assure this point. From now on, all the explanations will be based on the Binomial model.

@@

\subsection{Rao-Blackwellized Coverage Probability}
Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were given at first (see 5.1) and $z_{ij}$ is a sufficient statistic. This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-th player's interval estimates on the $i$-th dataset. We can calculate this probability  because we know the distribution of $p_{ij} \vert z_{ij}, r, \beta$ in (9). Note that conditioning on $z_{ij}$ is equivalent to conditioning on $\mathbf{z}$ because we know $r$ and $\beta$. Then, we can estimate the first player's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$, which is way more accurate than the previous one.
\section[Example]{Example}
\subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
Suppose you live in the New York state (NY) and have been suffering from severe coronary heart disease (hopefully not). If you are supposed to receive the coronary artery bypass graft (CABG) surgery soon, you might want to find the most famous hospital for dealing with such a surgery. On top of that, if you can figure out each hospital's abililty to handle this surgery, it will be useful for your decision to choose a hospital.
\\

@@

The multi-level modeling that assumes a bigger population-level hierarchy will be insightful in this problem. Here, we presume a state-level (NY) hierarchy governing the true death rates of CABG surgery of all the hospitals in NY. This perspective is to view the true death rates of those 31 hospitals as sampled from the state-level population distribution whose mean is 0.02. For reference, a model check can be useful for evaluating the validity of such a view point (Christiansen and Morris, 1996). 
\\

Assuming an additional hierarchy is reasonable, a model-fitting process begins.  Since the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) looks relatively much bigger than the number of deaths ($z_{j}$), the Poisson distribution would be our first choice to describe the uncertainty in our data. Next, \code{gbp} will help us fit the Poisson multi-level model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.02 ($\lambda_{0}=0.02$) as described in 3.2 . For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via any regression.
\begin{CodeChunk}
\begin{CodeInput}
R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "pr")
R> p
\end{CodeInput}
\begin{CodeOutput}
Summary for whole observations:

@@

  post.mode.alpha post.sd.alpha
1          -5.818         0.411
\end{CodeOutput}
\end{CodeChunk}
Since estimated $\alpha$ is -5.818, we can easily calculate $r=\textrm{exp}(5.818)=336$, which will be helpful for understanding how each shrinkage of hospital was determined by comparing this value to the amount of observed information ($n_{j}$).
\\

@@

Intuitively, the result of multi-level modeling makes more sense than that of naive sample mean. For example, suppose there are two hospitals, whose sample means ($z_{j} / n_{j}$) are 0 and 0.01 and caseloads ($n_{j}$) are 1 and 100 each. Do you believe that the former hospital is better than the latter and are you going to choose the former hospital? Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge its true death rate per exposure with just one caseload. Though somewhat extreme, this is what happens for the two left-most hostpitals on the first plot and this is why hierarchical modeling is a reasonable choice for this dataset.
\\

The estimated 95\% intervals are displayed on the right-side plot. We can clearly see that all the posterior means (red dots) are between sample mean (empty dots) and second-level mean (a blue horizontal line). Overall, as the caseload (size of dots) increases towards the right and as the posterior mean gets closer to 0, the length of interval gets shorter, which the formula of posterior variance in (6) implies. But the most important information from this plot would be the visualized range of each hospital's true death rate per exposure. 
\\

@@

\begin{CodeChunk}
\begin{CodeInput}
R> shr <- seq(0.01, 0.99, length.out = 20)
R> r.trial <- mean(n) * shr / (1 - shr)
R> cov.save <- sapply (1 : length(r.trial), function(i){
R>               coverage(p, A.or.r = r.trial[i], mean.PriorDist = 0.02, 
R>                        nsim = 500)$average.coverageRB
R>             })
R> plot(shr, cov.save, type = "l", ylim = c(0.8, 1), xlab = "Shrinkage",
R>      ylab ="", main = "Rao-Blackwellized Coverage Estimate", lwd = 3,
R>      col = 2)
R> abline(h = 0.95)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 5.5cm]{hospital3.png}
\end{center}
\end{figure}

This plot shows that the estimated shrinkages are at least 0.947 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval. Note that our model is approximating the true distribution of shrinkage by ADM (see 4.2). Considering this point, we finally conclude that the interval estimates from the suggested multi-level modeling on this particular dataset has a very good repeated sampling property.
\\

@@

First of all, the independent Binomial distribution given a true batting average of each player (see (7)) seems an appropriate probability distribution describing the uncertainty in this dataset. Assuming this distribution, we know that the sample mean (MLE) has many nice properties, one of which is uniformly minimum variance unbiased estimator (UMVUE), and is the simplest way to estimate their true batting averages. Can we say this is the best way to predict their batting averages?
\\

Efron and Morris (1975) said ``no,'' and suggested James-Stein estimator, making each players' sample mean shrink towards an estimated mean of the second-level prior distribution. They showed that this estimator was more than three times efficient than the sample mean under squared error loss. On top of that, a few years later Morris (1983) introduced interval estimates that could successfully catch the batting averages over the remaining season, which the MLE and its interval estimate could not.
\\

Our hierarchical modeling is a sequel to these researches, which can add one more unique value. Suppose you strongly believe that the outfielder's batting averages should be different from other positions' ones, not giving a credit to the assumption that all players' batting averages shrink towards the same mean. Instead, you want to assume two different second-level hierarchies for outfielders and for other positions, within each of which sharing information and regressing toward the mean (RTTM) occur. This perspective considers true batting averages of outfielders as sampled from the one and those of other positions from the other. Our multi-level modeling provides a way to incorporate such information (covariate) seamlessly into the second-level hierarchy.
\begin{CodeChunk}
\begin{CodeInput}
R> b <- gbp(z, n, x, model = "br")
R> b
\end{CodeInput}
\begin{CodeOutput}
Summary for whole units:

@@

However, achieving at least 95\% coverage at specific true values of ($r$ and $\beta$) does not mean that our model has good repeated sampling property. So, as we did in previous examples, we will see whether coverage probabilities are at least 0.95 when the true shrinkage value ($B(r)$) varies, fixing $\beta$ at estimated values. Note that, if we want to check a coverage probability under the different parameter values, $r$ and $\beta$, for example 150 for $r$ and $(-1, 0.5)^{T}$ for $\beta$, the appropriate code is \code{R> coverage(b, A.or.r = 150, reg.coef = c(-1, 0.5), covariates = x, nsim = 10000)}.

\begin{CodeChunk}
\begin{CodeInput}
R> shr <- seq(0.01, 0.99, length.out = 20)
R> r.trial <- mean(n) * shr / (1 - shr)
R> cov.save <- sapply (1 : length(r.trial), function(i){
R>               coverage(b, A.or.r = r.trial[i], reg.coef = c(-1.194, 0.389), 
R>                        covariates = x1, nsim = 500)$average.coverageRB
R>             })
R> plot(shr, cov.save, type = "l", ylim = c(0.8, 1), xlab = "Shrinkage",
R>      ylab ="", main = "Rao-Blackwellized Coverage Estimate", lwd = 3,
R>      col = 2)
R> abline(h = 0.95)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 5.5cm]{baseball4.png}
\end{center}
\end{figure}

This plot shows that the estimated shrinkages are at least 0.946 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval. Note that even this result does not guarantee good repeated sampling property because $\beta$ was fixed. But, this result can definitely be an encouraging sign for our model's good repeated sampling property. 
\\

>>>>

%% an abstract and keywords
\Abstract{Bayesian-frequentist reconciliation via Bayesian hierarchical modeling for Gaussian, Binomial, and Poisson data and frequentist method check for good coverage probability.}
\Keywords{hierarchical model, multilevel model, random effects mixed model, method check, coverage probability, normal, binomial, poisson, shrinkage, \proglang{R}}
\Plainkeywords{keywords, comma-separated, not capitalized, r} %% without formatting
%% at least one keyword must be supplied

@@

\section[Feasible Data Types]{Three Feasible Types of Data }
This package is intended to fit a multilevel model on the group-level (or unit-level) data in which each group-level (or unit-level) observation is believed to have the Normal, Poisson, or Binomial distribution. In this section, we will introduce three specific types of feasible datasets.

@@

\section[Multilevel Structure]{Multilevel Structure}
Our multilevel model, also called a conditionally independent hierarchical model (Kass and Steffey, 1989), is a very powerful tool for exploring the hierarchical sturucture in data. For example, we can think about a district-level hierarchy (bigger population) for 8 schools, the state-level hierarchy for 31 hospitals, and the position-level hierarchy for 18 baseball players. \code{gbp}, one of functions in \pkg{Rgbp}, fits such a hierarchical model whose first-level hierarchy has a distribution of observed data and second-level (bigger population hierarchy) has a conjugate prior distribution on the first-level parameter. Users can determine one of three types of multilevel models, such as Normal-Normal, Poisson-Gamma, and Binomial-Beta, based on their datasets. 
\\

@@

where $\mu_{0j} =x^{T}_{j}\beta,~j=1, \ldots, 8$, $x_{j}$ is $j$-th school's covariate vector ($m\times 1$), and $m$ is the number of regression coefficients. Note that if there is no covariate then $x_{j, (1\times1)}=1$ for an intercept term and so $\mu_{0j}=\mu_{0}=\beta_{0}$ for all $j$, resulting in an exchangeable prior distribution. For reference, a paramter with a zero subscript, such as $\mu_{0j}$, represents a mean parameter of the prior (second-level) distribution, \emph{i.e.}, a prior mean. Also,  based on this conjugate prior distribution, it is easy to derive corresponding posterior distribution, which is the same as (1) $\times$ (2) up to a normalizing constant.
\begin{equation}
\mu_{j}\vert \textbf{y}, \beta, A \stackrel{ind}{\sim}\textrm{Normal}(~(1-B_{j})y_{j} + B_{j}\mu_{0j},~(1-B_{j})\sigma^{2}_{j}),
\end{equation}
where $B_{j}\equiv\sigma^{2}_{j}/(\sigma^{2}_{j} + A),~j=1, \ldots, 8$, are called shrinkages.

\subsection[Poisson-Gamma]{Poisson-Gamma}
\code{gbp} is also able to build a Poisson-Gamma multilevel model on the 31 hospital data. Note that a constant, $1/r$, multiplied to the Gamma distribution below is a scale and a square bracket below indicates [mean, variance] of distribution. And for notational consistency, let's define $y_{j}\equiv z_{j} / n_{j}$ for all $j$.
\begin{equation}
z_{j}\vert \lambda_{j} \stackrel{ind}{\sim}\textrm{Poisson}(n_{j}\lambda_{j}),
\end{equation}
\begin{equation}
\lambda_{j}\vert \beta, r\stackrel{ind}{\sim}\frac{1}{r}\textrm{Gamma}(\lambda_{0j}r)\sim \textrm{Gamma}[\lambda_{0j}, ~\frac{\lambda_{0j}}{r}],
\end{equation}

@@

\subsection[ADM]{Adjustment for Density Maximization}
When it comes to estimating a shrinkage, we can notice that it is a function of the second-level variance component, \emph{i.e.}, $B_{j}\equiv\sigma^{2}/(\sigma^{2}+A)=B_{j}(A)$ for Gaussian and $B_{j}\equiv r/(r+n_{j})=B_{j}(r)$ for Poisson and Binomial models.
\\

In this case, the most common way is to obtain an MLE of the variance component with its asymptotic Normality and then to use Delta method for asymptotic Normal distribution of shrinkage, \emph{i.e.}, $\hat{B}_{j, MLE}=B_{j}(\hat{A}_{MLE})$. But is the Normal approximation a good approximation for shrinkage that takes on a value between 0 and 1? If it is, why do we fit a logistic regression, such as logit($p$) = $x^{T}\beta$, instead of fitting a linear regression, $p = x^{T}\beta+\epsilon$?
\\

Here the adjustment for density maximization (Morris and Tang, 2011), called ADM, comes. It assumes the Beta distribution for shrinkage because this distribution is also defined between 0 and 1. In the end, ADM  estimates its posterior moments, \emph{i.e.}, $E(B_{j}\vert\textrm{data})$ and $Var(B_{j}\vert\textrm{data})$, without any trouble that MLE can cause. Please refer to Morris and Tang (2011) for more apparent advantages of ADM.
\\

@@

There are two kinds of model justification process; one is a model check and the other is a method check. The model check is for the justification of a hierarchical modeling on a specific dataset. One possible question is, ``Can this dataset benefit from such a multilevel modeling?'' Christiansen and Morris (1996) answered this question by using a mixture model, $z_{j}\vert \beta, r\sim\textrm{Negative-Binomial}$, on Poisson data to justify the second-level hierarchy. They found that their data had more variation than expected of the first-level Poisson distribution and Poisson hierarchical model could successfully account for such additional variation.
\\

Once we are sure that the hierarchical modeling can be appropriate for our data, the following quetsion will be about the validity of interval estimates, the final product of this multilevel modeling. ``Does the 95\% (can be specified differently) confidence interval obtained via this Bayesian model-fitting process achieve 95\% confidence level  for any true parameter values?'' Our answer is ``yes'' and \pkg{Rgbp} has a function to assure this point. From now on, all the explanations will be based on the Binomial model.

@@

\subsection{Rao-Blackwellized Coverage Probability}
Based on the definition of Rao-Blackwellization, we define $E(I_{ij}\vert z_{ij}, r, \beta$), where $r$ and $\beta$ were given at first (see 5.1) and $z_{ij}$ is a sufficient statistic. This expectation is the same as Pr$(\hat{p}_{ij, low}\le p_{ij} \le\hat{p}_{ij, upp}\vert z_{ij}, r, \beta)$, where ($\hat{p}_{ij, low}$, $\hat{p}_{ij, upp}$) is $j$-th player's interval estimates on the $i$-th dataset. We can calculate this probability  because we know the distribution of $p_{ij} \vert z_{ij}, r, \beta$ in (9). Note that conditioning on $z_{ij}$ is equivalent to conditioning on $\mathbf{z}$ because we know $r$ and $\beta$. Then, we can estimate the first player's coverage probability by $\sum_{i=1}^{500}E(I_{i1}\vert z_{i1}, r, \beta)/500$, which is more accurate than the previous one.

\section[Example]{Example}
\subsection[Known Second-level Mean]{31 Hospitals: Known Second-level Mean}
Suppose you live in the New York state (NY) and have been suffering from severe coronary heart disease (hopefully not). If you are supposed to receive the coronary artery bypass graft (CABG) surgery soon, you might want to find the most famous hospital for dealing with such a surgery. On top of that, if you can figure out each hospital's abililty to handle this surgery, it will be useful for your decision to choose a hospital.
\\

@@

The multilevel modeling that assumes a bigger population-level hierarchy will be insightful in this problem. Here, we presume a state-level (NY) hierarchy governing the true death rates of CABG surgery of all the hospitals in NY. This perspective is to view the true death rates of those 31 hospitals as sampled from the state-level population distribution whose mean is 0.02. For reference, a model check can be useful for evaluating the validity of such a view point (Christiansen and Morris, 1996). 
\\

Assuming an additional hierarchy is reasonable, a model-fitting process begins.  Since the true death rate per exposure after CABG surgery might be small and the caseload ($n_{j}$) is much bigger than the number of deaths ($z_{j}$), the Poisson distribution would be our first choice to describe the uncertainty in our data. Next, \code{gbp} will help us fit the Poisson multilevel model with the Gamma conjugate prior distribution on the true death rate $\lambda_{j}$ whose mean is 0.02 ($\lambda_{0}=0.02$) as described in 3.2 . For reference, the number of regression coefficients ($m$) is 0 because we do not need to estimate the prior mean via any regression.
\begin{CodeChunk}
\begin{CodeInput}
R> p <- gbp(z, n, mean.PriorDist = 0.02, model = "pr")
R> p
\end{CodeInput}
\begin{CodeOutput}
Summary for whole observations:

@@

  post.mode.alpha post.sd.alpha
1          -5.818         0.411
\end{CodeOutput}
\end{CodeChunk}
Since estimated $\alpha$ is -5.818, we can easily calculate $\hat{r}=\textrm{exp}(5.818)=336$, which will be helpful for understanding how each shrinkage was determined by comparing this value to the amount of observed information ($n_{j}$).
\\

@@

Intuitively, the result of multilevel modeling makes more sense than that of naive sample mean. For example, suppose there are two hospitals, whose sample means ($z_{j} / n_{j}$) are 0 and 0.01 and caseloads ($n_{j}$) are 1 and 100 each. Do you believe that the former hospital is better than the latter and are you going to choose the former hospital? Borrowing information from state-level hierarchy seems reasonable for the former hospital because it is hard to judge its true death rate per exposure with just one caseload. Though somewhat extreme, this is what happened to the two left-most hostpitals in the first plot and this is why hierarchical modeling is a reasonable choice for this dataset.
\\

The estimated 95\% intervals are displayed on the right-side plot. We can clearly see that all the posterior means (red dots) are between sample mean (empty dots) and second-level mean (a blue horizontal line). For reference, if we want to draw this plot by the order of data input, \code{plot(p, sort = FALSE)} is a right adjustment. Overall, as the caseload (size of dots) increases towards the right and as the posterior mean gets closer to 0, the length of interval gets shorter, which the formula of posterior variance in (6) implies. But the most important information from this plot would be the visualized range of each hospital's true death rate per exposure. 
\\

@@

\begin{CodeChunk}
\begin{CodeInput}
R> shr <- seq(0.01, 0.99, length.out = 20)
R> r.trial <- mean(n) * shr / (1 - shr)
R> cov.save <- sapply (1 : length(r.trial), function(i){
R>               coverage(p, A.or.r = r.trial[i], mean.PriorDist = 0.02, 
R>                        nsim = 500)$average.coverageRB
R>             })
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 5.5cm]{hospital3.png}
\end{center}
\end{figure}

We plotted \code{cov.save} on \code{shr}, connecting dots. This plot shows that the estimated shrinkages are at least 0.947 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval. Note that our model is approximating the true distribution of shrinkage by ADM (see 4.2). Considering this point, we finally conclude that the interval estimates from the suggested multilevel modeling on this particular dataset has a very good repeated sampling property.
\\

@@

First of all, the independent Binomial distribution given a true batting average of each player (see (7)) seems an appropriate probability distribution describing the uncertainty in this dataset. Assuming this distribution, we know that the sample mean (MLE) is an uniformly minimum variance unbiased estimator (UMVUE) with nice properties. And it is the simplest one to estimate their true batting averages. But can we say this is the best way to predict their batting averages?
\\

Efron and Morris (1975) said ``no,'' and suggested James-Stein estimator, making each players' sample mean shrink towards an estimated mean of the second-level prior distribution. They showed that this estimator was more than three times efficient than the sample mean under squared error loss. On top of that, a few years later Morris (1983) introduced interval estimates that could successfully catch the batting averages over the remaining season, which MLE and its interval estimate could not.
\\

Our hierarchical modeling is a sequel to these researches, which can add one more unique value. Suppose you strongly believe that the outfielder's batting averages should be different from other positions' ones, not giving a credit to the assumption that all players' batting averages shrink towards the same mean. Instead, you want to assume two different second-level hierarchies for outfielders and for other positions, within each of which sharing information and regressing toward the mean (RTTM) occur. This perspective considers true batting averages of outfielders as sampled from the one and those of other positions from the other. Our multilevel modeling provides a way to incorporate such information (covariate) seamlessly into the second-level hierarchy.
\begin{CodeChunk}
\begin{CodeInput}
R> b <- gbp(z, n, x, model = "br")
R> b
\end{CodeInput}
\begin{CodeOutput}
Summary for whole units:

@@

However, achieving at least 95\% coverage at specific true values of $r$ and $\beta$ does not mean that our model has good repeated sampling property. So, as we did in previous examples, we will see whether coverage probabilities are at least 0.95 when the true shrinkage value ($B(r)$) varies, fixing $\beta$ at estimated values. Note that, if we want to check a coverage probability under the different parameter values, $r$ and $\beta$, for example 150 for $r$ and $(-1, 0.5)^{T}$ for $\beta$, the appropriate code is \code{R> coverage(b, A.or.r = 150, reg.coef = c(-1, 0.5), covariates = x, nsim = 10000)}.

\begin{CodeChunk}
\begin{CodeInput}
R> shr <- seq(0.01, 0.99, length.out = 20)
R> r.trial <- mean(n) * shr / (1 - shr)
R> cov.save <- sapply (1 : length(r.trial), function(i){
R>               coverage(b, A.or.r = r.trial[i], reg.coef = c(-1.194, 0.389), 
R>                        covariates = x1, nsim = 500)$average.coverageRB
R>             })
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 5.5cm]{baseball4.png}
\end{center}
\end{figure}

We drew \code{cov.save} on \code{shr}, conneting dots. It shows that the estimated shrinkages are at least 0.946 on the tried range of true shrinkage values, slightly deviating from the definition of 95\% confidence interval. Note that even this result does not guarantee good repeated sampling property because $\beta$ was fixed. But, this result can definitely be an encouraging sign for our model's good repeated sampling property. 
\\
